---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

library(tidyverse)
logged_data <- read.csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRxbgYxXkPRjmz-fsJwB-gvKhvC6KGYxeKXQK3zEBTl0gwx2Vbfec_Wb7XCypSgNeLaH2InMP4cJgqh/pub?gid=2070540705&single=true&output=csv")

latest_data <- logged_data %>%
  rename(screen_hours = 3,
        num_one_app  = 4,
        main_time_of_day  = 5,
        day_of_week = 6)
rounded_data = round(latest_data$screen_hours)
#least hours 
least_hours <- min(rounded_data)
#max_hours
max_hours <- max(rounded_data)
```

```{css}

body {
  background-color: white;
  font-family: "Playfair Display", serif;
}

h2 {
  color: #black;
}
```

## Patterns in screen use behavior

This is a self reported screen time behavior data. The data set contains categorical and numerical variables related to individuals digital device usage patterns.

## Screen Time Distribution

```{r}
paste("These are the minimum and maximum screen time reported (rounded to the nearest hour): I analysed the least number of screen time in a day which is", least_hours ,"hour and the maximum screen time in is", max_hours , "hours.")
```

These are the minimum and maximum screen time reported (rounded to the nearest hour): I analysed the least number of screen time in a day which is `r least_hours` hours and the maximum screen time in is `r max_hours` hours.

## Daily patterns

This bar chart shows the most common screen time of the day, when I predominantly use my phone throughout the day (morning, afternoon, evening, night)

```{r}
#Most Common Screen Time of Day (bar graph)
ggplot(latest_data, aes(y = main_time_of_day)) +
  geom_bar(fill = "honeydew")+
    labs(title = "Most Common Screen Time of Day",
       subtitle = "The peak screen use periods throughtout the day",
       x = "Number of responses",
       y = NULL) +
        theme(plot.background = element_rect(fill = "honeydew"),
          panel.background = element_rect(fill = "darkgrey"),
          text = element_text(color = "black"))

largest_time <- latest_data %>%
  count(main_time_of_day) %>%
  arrange(desc(n)) %>%
  slice_head(n = 1)

```

In this bar chart of most common screen time of the day, it is pretty obvious that i use my phone during the `r largest_time` responses, the most. This is most likely due to the fact that during the evenings i wind down and get ready for bed, and this usually comprises of me scrolling or watching a video to sleep to💤.

## Weekly patterns

This bar chart shows the weekly patterns in phone usage behavior. Analyzing whether i used my phones more during weekends or weekdays. This bar chart gets the average (mean) number of screen hours reported for each day of the week.

```{r}
#Average screen hours by day
latest_data %>%
  group_by(day_of_week) %>%
  summarise(avg_screen_hours = mean(screen_hours, na.rm = TRUE)) %>%
  ggplot(aes(x = day_of_week, y = avg_screen_hours)) +
  geom_bar(stat = "identity", fill = "lightyellow") +
  labs(title = "Screen time by day of week",
       subtitle = "Average screen hours per day",
       x = "Day of Week",
       y = "Average Screen Hours") +
  theme(plot.background = element_rect(fill = "lightyellow"),
        panel.background = element_rect(fill = "darkgrey"),
        text = element_text(color = "black"))

day_average <- latest_data %>%
  group_by(day_of_week) %>%
    summarise(avg_screen_hours = mean(screen_hours, na.rm = TRUE))

highest_day <- day_average %>%
  arrange(desc(avg_screen_hours)) %>%
  slice_head(n = 1)

highest_day_name <- highest_day$day_of_week
highest_day_hours <- round(highest_day$avg_screen_hours, 1)

```

In this bar chart of screen time by day of week, the average screen hours is higher for `r highest_day_name` with an average of `r highest_day_hours` hours. This may be due to the fact that i use my phone more scrolling in bed or just leisurely watching something in bed 😭. I know its probably not the most productive thing i could be doing during the weekends.
